<!-- rmarkdown v1 -->
Exploring Overlap
=================================================
This report looks explores the overlap of genes between basins

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of two directories.-->
```{r, echo=F, message=F} 
# cat("Working directory: ", getwd())

  knitr::opts_knit$set(root.dir='../../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# cat("Working directory: ", getwd())
library(knitr)
opts_chunk$set(
  results='show', 
  comment = NA, 
  tidy = FALSE,
  fig.width = 6.5, 
  fig.height = 4, 
  fig.path = 'Figures/'
)
# dpi = 400,
# out.width = "650px", #This affects only the markdown, not the underlying png file.  The height will be scaled appropriately.

echoChunks <- TRUE
options(width=120) #So the output is 50% wider than the default.
read_chunk("./Analysis/GeneticOverlap/GeneticOverlap.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```
<!-- Load the packages.  Suppress the output when loading packages. --> 
```{r LoadPackages, echo=echoChunks, message=FALSE}
```

<!-- Load any Global functions and variables declared in the R file.  Suppress the output. --> 
```{r DeclareGlobals, echo=echoChunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. --> 
```{r, echo=echoChunks, message=FALSE}
```

<!-- Load the datasets.   -->
```{r LoadData, echo=echoChunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r TweakData, echo=echoChunks, results='show', message=FALSE}
```

# Calculate Overlap
```{r CalculateOverlap, echo=echoChunks, message=TRUE}
```

# Venn Diagrams
The Venn diagrams are [available to download on GitHub](https://github.com/LiveOak/LylesCoalbedMethane2/tree/master/Analysis/GeneticOverlap/Figures) as tiff files.

```{r PlotVennDiagrams, echo=F, message=F, fig.width = 8, fig.height = 8}
```

# Display Table

To [download the CSV](https://github.com/LiveOak/LylesCoalbedMethane2/blob/master/Data/Derived/GeneByBasin.csv), please go to `r pathOutputGenesByBasin` at [https://github.com/LiveOak/LylesCoalbedMethane2](https://github.com/LiveOak/LylesCoalbedMethane2).

```{r DetermineIntersection, echo=echoChunks, message=TRUE, results='asis'}
```

```{r display-table, echo=echoChunks, message=TRUE, results='asis'}
```

# Session Information
For the sake of documentation and reproducibility, the current report was build on a system using the following software.

```{r session_info, echo=FALSE}
cat("Report created by", Sys.info()["user"], "at", strftime(Sys.time(), "%Y-%m-%d, %H:%M %z"))
sessionInfo()
```
